Temporal Dynamics of Normalization Reweighting

### 2023-07-31 manuscript.Rmd
Revert to processing level 1

processdata <- 2  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data (requires 0.4GB of storage)
# 2 - download processed individual data and analyse (requires 11.5GB of storage)
# 3 - download all raw data and analyse (requires 143GB of storage)

>>>>

processdata <- 1  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data (requires 0.4GB of storage)
# 2 - download processed individual data and analyse (requires 11.5GB of storage)
# 3 - download all raw data and analyse (requires 143GB of storage)
